Application-Level Regression Testing Framework using Jenkins

### 2017-03-07 manuscript/manuscript.tex
Cleaned up text

\subsection{Configuration Choices}
Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restricting access to the physical VM and Jenkins GUI (bwjenkins) utilizing iptables, SSL and OTP.  A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console. All the configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted. \\
(config file snippets below)

@@

\section{Anatomy of A Test}
\label{sec:TestAnatomy}

@@

\subsection{SWTools with Lammps}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{swtools-lammps-jenkins}
\caption{ SWTools with Lammps }
\label{fig:swtools-lammps-jenkins}
\end{figure}

>>>>

\subsection{Configuration Choices}
Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with pass-wordless access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restricting access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.  A reverse proxy was used to run Jenkins behind apache/http with SSL for access to the administrative console. All the configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted. \\
(config file snippets below)

@@

\section{Anatomy of A Test}
\label{sec:TestAnatomy}
New software projects are required to be tested on our TDS and approved before deployment on Blue Waters.

@@

\subsection{SWTools with Lammps}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{swtools-lammps}
\caption{ SWTools with Lammps }
\label{fig:swtools-lammps}
\end{figure}
